### 2021-10-06 plos_latex_template.tex
minor changes - Batool

Investing more in effort in the most excluded groups does not mean neglecting the others (see \textbf{Rule \ref{rule_inclusion}} for more on that). 
But it will prevent from falling into the mistake of treating diversity as a checklist.
It will also guide the vision of diversity for your conference--and your strategies to achieve it:
Will a more diverse conference translate into an even gender distribution in your speakers? 
Would it be the presence of racialized people --especially Black people-- among the head organizers, speakers, and attendees? 
Would it be having LGBTQIA+ friendly-spaces or community participation from key geographic regions?
This exercise will also help coming up with indicators that would help the organizing team assess the fulfillment of the diversity objectives along the way.

@@

Conferences are among the least accessible spaces that people with disabilities may encounter \cite{priceAccessImaginedConstruction2009}.
Importantly, accessibility practices are inclusive not only for people with disabilities but can be beneficial to a broad spectrum of people. For instance, having captions is helpful to deaf and hard-of-hearing people, non-native speakers, and everyone in general. 
% Liz: I don't think it's actually ironic. maybe surprising or counterintuitive? ast: absolutely! i put importantly at the end to highlight that without opposition

If the conference is in person, the venue must be accessible for people with mobility limitations. 
% Liz: let's stay away from deficit-model language like "limitations." Possible aternatives:
% people who use wheelchairs or other assistive mobility devices
% ... must be physically accessible for disabled people

Accommodations such as a quiet space for neurodivergent people should also be provided.
% Liz: I hate "accommodateions because it sounds like something optional or for comfort or luxurious Consider something like "facilities"?

@@

Meeting the need 
% Liz: People with disabilities don't want to be considered "needy". We reject the term "special needs" in part because it frames the person with the disability as being the burden causing the accommodation, where maybe it's the responsibility of society to be open to everyone. So I wonder if it's the same for people who speak other languages. Maybe they are not needy or inferior.  Or maybe it's wrong for me to apply disability rights philosophy to language.
% The linguistic diversity of conference participants is often overlooked,
% resulting in missed opportunities for them, as well as for the conference
% to benefit from their contributions.

of linguistically diverse audience is an important aspect in inclusion that is often overlooked.

 Non-native English speakers may feel intimidated to ask questions or raise their views. Providing a welcoming and diverse environment by encouraging the full participation of those individuals is critical (Rule 2). If the panelist or speakers will not be presenting in their native language, it may helpful to rephrase audience questions in a less complex language. Consider letting speakers know in advance that they can ask for a question to be translated to them in their native language and that they can respond in their native language.

@@

As you design the promotion plan, actively reach out and promote the conference to people who have been systematically excluded. If part of the community has been historically discriminated against, one should emphasize that they are particularly welcome in this event and that the organization will make it a safe and inclusive environment. This could through publishing the diversity statement (e.g., https://user2021.r-project.org/about/diversitystatement/), the code of conduct and accessibility guidelines, and providing fee waivers and financial support. People who fear getting rejected when applying for scholarships and waivers may find it relieving that the process will be supportive rather than discriminatory. If possible, include representative from these communities within the organizing team (rule \ref{rule_inclusion}). Also, try to advertise the conference in multiple languages (rule \ref{rule_language}) and express this welcoming spirit in your communication strategy (social networks, website, brand, and visual identity) to let people know that they are seen, respected, and welcome; that this is their space and community too.

Always include explicit descriptions of accessibility and other inclusion practices (rule \ref{rule_accessibility}). Help people answer the question "Can I attend this conference?" without the emotional labor of contacting the organizers and be public about your commitment to equity and inclusions. Be careful with the language you use in promoting to the conference and how you talk about minoritized people, assertively set tone of inclusion. In addition to excluding derogatory or discriminatory language, make the effort to teach yourself the vocabulary and the best ways to communicate to account for every culture and situation. Do not expect people to teach you --it's not their role-- and accept feedback without being offended.

Although conference attendees should have ample opportunities to network with each other, having a diverse offer of networking opportunities that can appeal to people with different backgrounds, accessibility needs, and preferences can be challenging, especially if you have the mindset of organizing each activity for the complete pool of attendants. If you think of smaller activities that can reach specific groups, preferably co-lead by community leaders, these sessions can be more productive and successful, and even inclusive, than trying to organize one single activity that can please the whole community(Rule \ref{rule_unbias})). Some examples are the newbies sessions for first-timers, mixers lead by specific subgroups or communities, or leisure activities that reunite subgroups with the same interests: arts, exercise, sports, movies, etc.

>>>>

Investing more effort in the most excluded groups does not mean neglecting the others (see \textbf{Rule \ref{rule_inclusion}} for more on that). 
But it will prevent from falling into the mistake of treating diversity as a checklist.
It will also guide the vision of diversity for your conference--and your strategies to achieve it:
Will a more diverse conference translate into an even gender distribution in your speakers? 
Would it be the presence of racialized people --especially Black people-- among the head organizers, speakers, and attendees? 
Would it be having LGBTQIA+ friendly-spaces or community participation from key geographic regions?
This exercise will also help coming up with indicators that would help the organizing team assess the fulfillment of the diversity objectives along the way.

@@

Conferences are among the least accessible spaces that people with disabilities may encounter \cite{priceAccessImaginedConstruction2009}.
Importantly, accessibility practices are inclusive not only for people with disabilities but can be beneficial to a broad spectrum of people. For instance, having captions is helpful to deaf and hard-of-hearing people, non-native speakers, and everyone in general. 
% Liz: I don't think it's actually ironic. maybe surprising or counterintuitive? ast: absolutely! i put importantly at the end to highlight that without opposition
If the conference is in person, the venue must be accessible for people with mobility limitations. 
% Liz: let's stay away from deficit-model language like "limitations." Possible aternatives:
% people who use wheelchairs or other assistive mobility devices
% ... must be physically accessible for disabled people
Accommodations such as a quiet space for neurodivergent people should also be provided.
% Liz: I hate "accommodateions because it sounds like something optional or for comfort or luxurious Consider something like "facilities"?

@@

Meeting the need 
% Liz: People with disabilities don't want to be considered "needy". We reject the term "special needs" in part because it frames the person with the disability as being the burden causing the accommodation, where maybe it's the responsibility of society to be open to everyone. So I wonder if it's the same for people who speak other languages. Maybe they are not needy or inferior.  Or maybe it's wrong for me to apply disability rights philosophy to language.
% The linguistic diversity of conference participants is often overlooked,
% resulting in missed opportunities for them, as well as for the conference
% to benefit from their contributions.
of linguistically diverse audience is an important aspect in inclusion that is often overlooked. Non-native English speakers may feel intimidated to ask questions or raise their views. Providing a welcoming and diverse environment by encouraging the full participation of those individuals is critical (Rule 2). If the panelist or speakers will not be presenting in their native language, it may helpful to rephrase audience questions in a less complex language. Consider letting speakers know in advance that they can ask for a question to be translated to them in their native language and that they can respond in their native language.

@@

As you design the promotion plan, actively reach out and promote the conference to people who have been systematically excluded. If part of the community has been historically discriminated against, one should emphasize that they are particularly welcome in this event and that the organization will make it a safe and inclusive environment. This could through publishing the diversity statement (e.g., https://user2021.r-project.org/about/diversitystatement/), the code of conduct and accessibility guidelines, and providing fee waivers and financial support. People who fear getting rejected when applying for scholarships and waivers may find it relieving that the process will be supportive rather than discriminatory. If possible, include representatives from these communities within the organizing team (\textbf{Rule \ref{rule_inclusion}}). Also, try to advertise the conference in multiple languages (\textbf{Rule \ref{rule_language}}) and express this welcoming spirit in your communication strategy (social networks, website, brand, and visual identity) to let people know that they are seen, respected, and welcome; that this is their space and community too.

Always include explicit descriptions of accessibility and other inclusion practices (\textbf{Rule \ref{rule_accessibility}}). Help people answer the question "Can I attend this conference?" without the emotional labor of contacting the organizers and be public about your commitment to equity and inclusions. Be careful with the language you use in promoting to the conference and how you talk about minoritized people, assertively set tone of inclusion. In addition to excluding derogatory or discriminatory language, make the effort to teach yourself the vocabulary and the best ways to communicate to account for every culture and situation. Do not expect people to teach you --it's not their role-- and accept feedback without being offended.

As we mentioned previously, conference attendees should have ample opportunities to network with each other. However, having a diverse offer of networking opportunities that can appeal to people with different backgrounds, accessibility needs, and preferences can be challenging, especially if you have the mindset of organizing each activity for the complete pool of attendants. If you think of smaller activities that can reach specific groups, preferably co-lead by community leaders, these sessions can be more productive and successful, and even inclusive, than trying to organize one single activity that can please the whole community (\textbf{Rule \ref{rule_unbias}}). Some examples are the newbies sessions for first-timers, mixers lead by specific subgroups or communities, or leisure activities that reunite subgroups with the same interests: arts, exercise, sports, movies, etc.
